### 2023-05-15 paper/content.tex
Add abstract to the paper

Our approach relies in the premise of assuming the magnetic anomaly within
the data window is a response of a dipolar source.
The latter is true when working
with particle signals in the SD magnetic domain state since they are uniform magnetized particles with strong dipolar anomalies.
However, \cite{Nagy2017} reported that particles within the PSD domain can record the paleomagnetic field for longer (than SD ones) periods of time, being the stabler and also with strongly non-dipolar characteristics.
Therefore the application of the proposed algorithm to natural samples should fail for those PSD particles.
\cite{CortesOrtuno2022} give important insights about the matter, they showed that PSD state particles present more accurate inversion results when considering the non-dipole components for small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor distances the dipole as approximations are remarkably accurate, as the higher-order moments decay rapidly with distance and therefore have less
influence on the particle's magnetic signal.
Thus, our approach can be considered reasonable for working with both particle SD and PSD states signals.
The latter happens mainly due to the sensor height being usually greater than 5 $\mu m$, considering a particle on the immediate surface of the sample the higher-order moments are already quite attenuated, thus circumventing the prominent problems described for non-dipolar components.

@@

The test using a simple synthetic sample shows the great capability of the method by estimating not only the precise center positions but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise.
While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths.
The real sample data positively answered the question of the algorithm's ability to deal with thin sections of rocks.
But also, showed the acceptable capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal disparities even greater than predicted in the complex synthetic test.
We also assessed the quality of the fit between the predicted dipole model and the original magnetic data using two criteria: the coefficient of determination ($R^2$) and the signal-to-noise ratio (SNR).

>>>>

Our approach relies in the premise of assuming the magnetic anomaly within
the data window is a response of a dipolar source.
The latter is true when working
with particle signals in the SD magnetic domain state since they are uniform magnetized particles with strong dipolar anomalies.
However, \cite{Nagy2017} reported that particles within the PSD domain can record the paleomagnetic field for longer (than SD ones) periods of time, being the stabler and also with strongly non-dipolar characteristics.
Therefore the application of the proposed algorithm to natural samples should fail for those PSD particles.
\cite{CortesOrtuno2022} give important insights about the matter, they showed that PSD state particles present more accurate inversion results when considering the non-dipole components for small sample-sensor distances (\textless 1 $\mu$m), but for larger sensor distances the dipole as approximations are remarkably accurate, as the higher-order moments decay rapidly with distance and therefore have less
influence on the particle's magnetic signal.
Thus, our approach can be considered reasonable to work with both particle SD and PSD states signals.
The latter happens mainly due to the sensor height being usually greater than 5 $\mu m$, considering a particle on the immediate surface of the sample the higher-order moments are already quite attenuated, thus circumventing the prominent problems described for non-dipolar components. This is corroborated by our non-dipolar synthetic sample showing the almost complete attenuation of non-dipolar components at distances greater than 5 $\mu m$.

@@

The test using a simple synthetic sample shows the great capability of the method by estimating not only the precise center positions but also retrieving the magnetization directions and intensity even under the considerable effect of high-frequency noise, for both dipolar and non-dipolar sources.
While the complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths.
The real sample data positively answered the question of the algorithm's ability to deal with thin sections of rocks.
But also, showed the acceptable capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal disparities even greater than predicted in the complex synthetic test.
We also assessed the quality of the fit between the predicted dipole model and the original magnetic data using two criteria: the coefficient of determination ($R^2$) and the signal-to-noise ratio (SNR).
